---
title: 'Data Analysis'
author: 
output: 
  github_document:
    toc: yes
  #pdf_document:
  #  dev: cairo_pdf
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

```{r "env", message=FALSE, warning=F}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
source(here::here("src/lib/functions.R"))
#renv::snapshot()
```

```{r "get data"}
load(here("data/raw-private/cleaned_data_w1.RData"))
load(here("data/raw-private/cleaned_data_w4.RData"))
source(here("src/analysis/data_for_analysis_exp.R"))
save(d, file = here("data/intermediate/cleaned_experiment.RData"))
#make data in long format for "simplified: analyses
source(here("src/analysis/long_data.R"))
```

## Descriptives
```{r "vars", fig.width=12, fig.height = 6}
source(here("src/analysis/descriptives.R"))
pd2b #Fig 2 manuscript

pd5 #Fig 4 in manuscript

pd3a + pd3b + #addititonal check 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

```{r "vars2", fig.width=12, fig.height = 10}
pd1a + pd1b + #additional check 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

```{r "vars3", fig.width=12, fig.height = 8}
pd4a + pd4b + #with all social groups or validity for dichitomization?
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

## Experiment 
```{r "treatment-view", fig.width=12, fig.height=12, eval=T}
source(here("src/analysis/treatment.R"))
p1 + p2 +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

```{r "treatment-simple", fig.width=8, fig.height=6}
p3 #Fig X
```

```{r "balance-test"}
source(here("src/analysis/balance-test.R"))
bp
```

### H1a: Nostalgic messages will increase affective sentiment for ideological social in-groups.
### H1b: Messages mentioning scapegoats will increase affective sentiment for ideological social in-groups.
### H2a: Nostalgic messages will decrease affective sentiment for ideological social out-groups.
### H2b: Messages mentioning scapegoats will decrease affective sentiment for ideological social out-groups.

### For in- and out-groups pooled
```{r "testing-h-pooled", fig.width=12, fig.height=6,}
source(here("src/analysis/h1_exp.R"))
p1_h1
```

### Robustness1: Main analysis without people positioning themselves in the center
```{r "robustness1"}
source(here("src/analysis/h_nocenter.R"))
p1_h1_e
```

### Robustness2: For each social group (appendix)
```{r "testing-h", fig.width=12, fig.height=6, eval=T}
p1a_l + p1a_r +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

p1b_l + p1b_r +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

### Robustness3: Heterogenous treatments

#### Ideology
```{r "he-ideo-p", fig.width=12, fig.height=8, eval=T}
source(here("src/analysis/he_ideology_pooled.R"))
phe_i
```

```{r "he-ideo", fig.width=12, fig.height=12, eval=T}
source(here("src/analysis/he_ideology.R"))

p1e_l + p1e_r +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

p2e_l + p2e_r +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

#### Party Choice
```{r "he-vc-p", fig.width=12, fig.height=12, eval=T}
source(here("src/analysis/he_partychoice_pooled.R"))
phe_vc
```

```{r "he-vc", fig.width=12, fig.height=12, eval=T}
source(here("src/analysis/he_partychoice.R"))

p1e_l + p1e_r +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

p2e_l + p2e_r +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

#### Populist vs Non-Populist vote support
```{r "he-popvote", fig.width=12, fig.height=8, eval=T}
source(here("src/analysis/he_popvote_pooled.R"))
phe_pop
```

#### Low vs High Levels of Education
```{r "he-edu", fig.width=12, fig.height=8, eval=T}
source(here("src/analysis/he_edu_pooled.R"))
phe_edu
```

#### Gender
```{r "he-gender", fig.width=12, fig.height=8, eval=T}
source(here("src/analysis/he_gender_pooled.R"))
phe_gen
```